Draft Research pt1

### 2019-03-01 draftResearch_pt1.Rmd
Yahoo API interface
Rolled up Yahoo API interface to single method call by URL path
Trying some approaches for parsing yahoo api data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("R/yahoo_api.R")
library(tidyverse)
library(rlist)
```

# Position Eligibility

```{r}
get_json("users;use_login=1/games;game_keys=mlb/players") -> players

players %>%
  content() -> players_content

players_content$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]]$players[c(1:25)] -> players_list

players_list %>% rlist::list.stack()

players %>% list.load()

```

# Projection Data
